Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2018-09-13 article.Rnw
Report the errors instead of quadratic errors and make minor corrections

In order to assess the accuracy of the moment approximations
(\autoref{eqn:mean-approx}), \autoref{fig:approx-plot} presents the
squared errors for (a) expectation and (b) variance.  The squared errors
are $[\mu - \text{E}(Y)]^2$ for the expectation and
$[ \mu \exp(-\phi) - \text{Var}(Y)]^2$ for the variance. In both cases
$\text{E}(Y)$ and Var$(Y)$ were computed numerically using 500
terms\footnote{ E$(Y) \approx \sum_{y=0}^{500}yp(y)$ and
  E$(Y^2) \approx \sum_{y=0}^{500}y^2p(y)$.}. The dotted lines represent
the border between the regions $\nu \leq 1$ and $\lambda > 10^\nu$, in
the $\mu$ and $\phi$ scale.

<<approx-plot, fig.height=3, fig.width=6, out.width=".8\\textwidth", fig.cap="Squared errors for the approximation of the (a) expectation and (b) variance. Dotted lines represent the restriction for suitable approximations given by \\cite{Shmueli2005}.">>=
@

The results in \autoref{fig:approx-plot} show that the mean
approximation is accurate, the largest squared error, for the parameter
values evaluated, is $0.038$.  For the variance approximation, the
largest squared error was $XXX$ and it occurs for negative values of
$\phi$. Interestingly, the errors for the variance are larger for
negative values of $\phi$ and present no clear relation with $\mu$, as
opposed to the regions gives by \citet{Shmueli2005} ($\phi \leq 0$ and
$\mu > 10 - \frac{\exp(\phi) - 1}{2\exp(\phi)}$).

@@

Regarding the COM-Poisson$_\mu$ distribution, in
\autoref{fig:indexes-plot} we present the relationship between (a) mean
and variance, (b--c) the dispersion and zero-inflation indexes for
different values of $\mu$ and $\phi$, and (d) the heavy-tail index for
$\mu=25$ and different values of $y$ and $\phi$.
\autoref{fig:indexes-plot} shows that the indexes are slightly dependent
on the expected values and tend to stabilize for large values of
$\mu$. Consequently, the mean and variance relationship
\autoref{fig:indexes-plot}(a) is proportional to the dispersion
parameter $\phi$. In terms of moments, this leads to a specification
indistinguishable from the quasi-Poisson regression model. The
dispersion indexes in \autoref{fig:indexes-plot}(b) show that the
distribution is suitable to deal to dispersed counts, of course. For the
parameter values evaluated the largest DI was $XXX$ and smallest was
$XXX$. \autoref{fig:indexes-plot}(c) shows the COM-Poisson can handle
a limited amount of zero-inflation, in cases of overdispersion
($\phi < 0$). On the other hand, for $\phi > 0$ (underdispersion) this
distribution is suitable to deal with zero-deflated counts. Heavy-tail
indexes in \autoref{fig:indexes-plot}(d) indicate the distribution is in
general a light-tailed distribution, i.e. $\text{HT} \to 0$ for
$y \to \infty$.

>>>>

In order to assess the accuracy of the moment approximations
(\autoref{eqn:mean-approx}), \autoref{fig:approx-plot} presents the
errors for (a) expectation ($\mu - \text{E}(Y)$) and (b) variance
($\mu \exp(-\phi) - \text{Var}(Y)$). In both cases $\text{E}(Y)$ and
Var$(Y)$ were computed numerically using 500 terms\footnote{
  E$(Y) \approx \sum_{y=0}^{500}yp(y)$ and
  E$(Y^2) \approx \sum_{y=0}^{500}y^2p(y)$.}. The dotted lines represent
the border between the regions $\nu \leq 1$ and $\lambda > 10^\nu$, in
the $\mu$ and $\phi$ scale.

<<approx-plot, fig.height=3, fig.width=6, out.width=".8\\textwidth", fig.cap="Errors for the approximation of the (a) expectation and (b) variance. Dotted lines represent the restriction for suitable approximations given by \\cite{Shmueli2005}.">>=
@

The results in \autoref{fig:approx-plot} show that the mean
approximation is accurate, the largest (absolute) error, for the
parameter values evaluated, is $-0.197$.  For the variance
approximation, the largest error was $8.4$ and it occurs for negative
values of $\phi$. Interestingly, the errors for the variance are larger
for negative values of $\phi$ and present no clear relation with $\mu$,
as opposed to the regions gives by \citet{Shmueli2005} ($\phi \leq 0$
and $\mu > 10 - (\exp(\phi) - 1)/(2\exp(\phi))$).

@@

Regarding the COM-Poisson$_\mu$ distribution, in
\autoref{fig:indexes-plot} we present the relationship between (a) mean
and variance, (b--c) the dispersion and zero-inflation indexes for
different values of $\mu$ and $\phi$, and (d) the heavy-tail index for
$\mu=25$ and different values of $y$ and $\phi$.
\autoref{fig:indexes-plot} shows that the indexes are slightly dependent
on the expected values and tend to stabilize for large values of
$\mu$. Consequently, the mean and variance relationship
\autoref{fig:indexes-plot}(a) is proportional to the dispersion
parameter $\phi$. In terms of moments, this leads to a specification
indistinguishable from the quasi-Poisson regression model. The
dispersion indexes in \autoref{fig:indexes-plot}(b) show that the
distribution is suitable to deal to dispersed counts, of course. For the
parameter values evaluated the largest DI was $4.21$ and smallest was
$0.168$. \autoref{fig:indexes-plot}(c) shows the COM-Poisson can handle
a limited amount of zero-inflation, in cases of overdispersion
($\phi < 0$). On the other hand, for $\phi > 0$ (underdispersion) this
distribution is suitable to deal with zero-deflated counts. Heavy-tail
indexes in \autoref{fig:indexes-plot}(d) indicate the distribution is in
general a light-tailed distribution, i.e. $\text{HT} \to 0$ for
$y \to \infty$.
